FastSRM: A fast, memory efficient and identifiable implementation of the shared response model

### 2022-08-06 paper/main.tex
replace W_i by A_i

The complexity of Deterministic SRM is in $\bigO(\mathrm{n_{iter}} mpvn)$, where
 $\mathrm{n_{iter}}$ is the number of iterations.
%
We monitor the convergence by computing the $\ell_{\infty}$ norm of the
gradient.
%
Note that we can monitor the gradient without any increase in complexity.
%
Indeed, after the updates with respect to each mixing matrix have been
carried out, the gradient with respect to $(W_i)_{i=1}^m$ \textbf{XXX $(W_i)_{i=1}^m$ not introduced so far} is zero and therefore
to compute the $\ell_{\infty}$ norm of the gradient we only need the gradient
with respect to $S$: $m S - \sum_i A_i^{\top}\xb_i$ where the right hand side is
used in the updates of $S$.
%
The algorithm is stopped when the
gradient falls below a chosen tolerance.
%

>>>>

The complexity of Deterministic SRM is in $\bigO(\mathrm{n_{iter}} mpvn)$, where
 $\mathrm{n_{iter}}$ is the number of iterations.
%
We monitor the convergence by computing the $\ell_{\infty}$ norm of the
gradient.
%
Note that we can monitor the gradient without any increase in complexity.
%
Indeed, after the updates with respect to each mixing matrix have been
carried out, the gradient with respect to $(A_i)_{i=1}^m$ is zero and therefore
to compute the $\ell_{\infty}$ norm of the gradient we only need the gradient
with respect to $S$: $m S - \sum_i A_i^{\top}\xb_i$ where the right hand side is
used in the updates of $S$.
%
The algorithm is stopped when the
gradient falls below a chosen tolerance.
%
